Gozde and Liora Extension Project

### 2015-05-12 extension.Rmd
Added interpretation sentence, residuals plots

# Cleaning up data
data <- data %>%
  rename(ext_vote = rexvote,
         age_1 = age1, # (18–29 years)
         age_2 = age2, # (30–45 years)
         age_4 = age4, # (>65 years)
         edu_1 = mye1, # Education: middle/high
         edu_2 = mye2, # Education: university
         farmer_own = farmerown,
         left_right_scale = zlrs, # Left-Right Scale
         eu_neg = euschlecht, # Negative evaluation of EU membership of one's own country
         z_dem_satis = zsatisdmo, # Dissatisfied: Democracy
         dispro_elect = disp, # Disproportionality
         federalism = lfed1, # Decentralization
         z_asylumseeker = zasylumseekers,
         z_unemp = zsur, # Unemployment rate
         z_replacement = zreplacementrate, # Unemp benefits
         max_er = rmax) # Maximum toughness in extreme right discourse
```

@@

# Model 1: Adorno Thesis (Individual Characteristics and Value Orientations)
The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.  We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale.

@@

All Three Models

>>>>

# Cleaning up data
data <- data %>%
  rename(ext_vote = rexvote,
         age_1 = age1, # (18–29 years)
         age_2 = age2, # (30–45 years)
         age_4 = age4, # (>65 years)
         edu_1 = mye1, # Education: middle/high
         edu_2 = mye2, # Education: university
         farmer_own = farmerown,
         left_right_scale = zlrs, # Left-Right Scale
         eu_neg = euschlecht, # Negative evaluation of EU membership of one's own country
         z_dem_satis = zsatisdmo, # Dissatisfied: Democracy
         dispro_elect = disp, # Disproportionality
         federalism = lfed1, # Decentralization
         z_asylumseeker = zasylumseekers ,
         z_unemp = zsur, # Unemployment rate
         z_replacement = zreplacementrate, # Unemp benefits
         max_er = rmax) # Maximum toughness in extreme right discourse
```

@@

# Model 1: Adorno Thesis (Individual Characteristics and Value Orientations)
The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.  We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale. These variables are rather poor proxies for "personality traits and value orientations", but provide the closest approximation from our dataset.

@@

# Diagnostics on our three models #
The unit of analysis in each model is the individual. We wanted to apply a number of diagnostics to further test the predictive power of each model.

For model 1, we first plot fitted values vs. residuals. Since we have a categorical outcome, binned residual plots are more informative than regular plots for fitted values vs. residuals. Here we benefited greatly from this Stackexchange post: http://stats.stackexchange.com/questions/63566/unexpected-residuals-plot-of-mixed-linear-model-using-lmer-lme4-package-in-r. Then, we extract the predicted probability for an example case: a young unemployed single male who self-identifies as right-wing in Austria.

```{r}
plot(fitted(model_1), residuals(model_1),
  xlab = "Fitted Values", ylab = "Residuals")
  abline(h=0, lty=2) # Not very useful since the outcome is a catogorical variable and is not distributed normally.

library(arm) # To create binned plots for logistic models
binnedplot(predict(model_1), resid(model_1), cex.pts=1, col.int="black")

data_model1 <- data.frame(male = 1, age_1 = 1, age_2 = 0, age_4 = 0, edu_1 = 1, edu_2 = 0, farmer_own = 0, worker = 0, retired = 0, unemployed = 1, partner = 0, left_right_scale = max(data$left_right_scale, na.rm = T), country = "AT")

predict(model_1, data_model1, type = "response")
```

For model 2, we again plot residuals vs. fitted values. This time the predictions are clustered on the left side. We then extract the predicted probability for an individual who disapproves of EU and is not satisfied with democracy.

plot(fitted(model_2), residuals(model_2),
  xlab = "Fitted Values", ylab = "Residuals")
  abline(h=0, lty=2)

binnedplot(predict(model_2), resid(model_2), cex.pts=1, col.int="black")

data_model2 <- data.frame(eu_neg = max(data$eu_neg, na.rm = T), z_dem_satis = max(data$z_dem_satis, na.rm = T), country = "AT")

predict(model_2, data_model2, type = "response")
```

For model 3, after plotting fitted values vs. residuals, we look for predicted probability for an individual whose context of unemployment rates, unemployment benefits, number of asylum seekers, and salience and variance of right-wing issues is Austria's most extreme--most likely to vote for an extreme right party, according to the theory.

```{r}
plot(fitted(model_3), residuals(model_3),
  xlab = "Fitted Values", ylab = "Residuals")
  abline(h=0, lty=2)

binnedplot(predict(model_3), resid(model_3), cex.pts=1, col.int="black")

#max_z_asylumseekers <- max(data$z_asylumseeker, na.rm = T) #4.45935
#max_z_unemp <- max(data$z_unemp, na.rm = T) #12.2919
#max_z_asylumseeker_z_unemp <- max(data$z_asylumseeker:data$z_unemp, na.rm = T) #-0.2445196
#max_z_replacement <- max(data$z_replacement, na.rm = T) #32.96374
#max_z_replacement_z_unemp <- max(data$z_replacement:data$z_unemp, na.rm = T) #0.5738534
#max_z_replacement_z_asylumseeker <- max(data$z_replacement:data$z_asylumseeker, na.rm = T) #0.5738534

#data_model3 <- data.frame(max_z_asylumseekers, max_z_unemp, max_z_asylumseeker_z_unemp, max_z_replacement, max_z_replacement_z_unemp, max_z_replacement_z_asylumseeker, country = "AT")
#predict(model_3, data_model3, type = "response")
#We have thus far been unable to debug the above code such that we could generate a prediction.  However, we do have a binned residual plot for this model
```

The binned residual plots show the highest level of randomness for the second and third models, Parsons' and the group conflict theories.  This method would indicate that, contrary to our conclusions from the separation plots (see below), these models have the closest fit to the observed data.  However, all of these conclusions must be qualified:  the proxy variables available to us in this data set do not perfectly operationalize the theoretical models in question.

Conclusion: All Three Models
